Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems

### 2024-08-06 article.hid2-ub-cicd.ppam24.tex
use image naming
#1

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth]{\imagedir kub-workflow.pdf}
    \caption{Current Urban Building Workflow from localization to city energy simulation report.}
    \label{fig:kub-workflow}
\end{figure}

@@

\begin{wrapfigure}{R}{0.6\textwidth} % 'R' or 'L' for right or left, and width
\centering
\subfloat[LOD-0: a building is represented by its bounding box]{%
  \includegraphics[width=0.48\linewidth]{\imagedir buildings-lod0.png}
  \label{fig:building-lod0}
}
%\hfill % This ensures that the images are placed side by side
\subfloat[LOD-1: a building is represented by its ground footprint elevated to its height]{%
  \includegraphics[width=0.48\linewidth]{\imagedir buildings-lod1.png}
  \label{fig:building-lod1}
}\\ % Ends the line for the first row of figures

\subfloat[LOD-2: a building in full detail using BIM. Note that LOD-2 and LOD-1 are mixed.]{%
  \includegraphics[width=0.48\linewidth]{\imagedir buildings-lod2.png}
  \label{fig:building-lod2}
}
%\hfill
\subfloat[LOD-2: A zoom on the LOD-2 building.]{%
  \includegraphics[width=0.48\linewidth]{\imagedir buildings-lod2-zoom.png}
  \label{fig:building-lod2-zoom}
}

@@

\begin{wrapfigure}{R}{0.6\textwidth}
\centering
\subfloat[LOD-0\label{fig:city-strasbourg-lod0}]{%
  \includegraphics[width=0.4\textwidth]{\imagedir city-strasbourg-lod-0.png}
}
\hfill % Ensures that the images are placed side by side
\subfloat[LOD-1\label{fig:city-strasbourg-lod1}]{%
  \includegraphics[width=0.4\textwidth]{\imagedir city-strasbourg-lod-1.png}
}\\ % Ends the line for the first row of figures

\subfloat[LOD-1 terrain\label{fig:city-grenoble-terrain}]{%
  \includegraphics[width=0.4\textwidth]{\imagedir city-grenoble-terrain.png}
}

@@

The current version of our simulation framework has implemented case 0 and case 1. Cases 2 and 3 require a full conformal mesh, which is not yet available. Moreover, these partitioning strategies are costly, so we have planned to use other third-party tools, such as Zoltan2~\cite{the_zoltan2_team_zoltan2_nodate}, to improve efficiency.
\begin{wrapfigure}{R}{0.6\textwidth}
\centering
\subfloat[Partitioning Case 0\label{fig:city-strasbourg-lod0-parts}]{%
  \includegraphics[width=0.48\linewidth]{\imagedir city-strasbourg-lod0-parts.png}
}
%\hfill % Ensures that the images are placed side by side
\subfloat[Partitioning Case 1\label{fig:city-strasbourg-lod1-parts}]{%
  \includegraphics[width=0.48\linewidth]{\imagedir city-strasbourg-lod1-parts.png}
}
%\subfloat[Partitioning Case 3: Large scale\label{fig:city-ny-largescale}]{%
%  \includegraphics[width=0.4\textwidth]{\imagedir city-newyork-largescale.png}
%}
\caption{Mesh partitioning illustrations}
\label{fig:partitioning}
\end{wrapfigure}

@@

\begin{figure}[htbp]
\centering
\subfloat[View on whole 3D mesh\label{fig:city-ny-largescale-whole}]{%
  \includegraphics[width=0.45\textwidth]{\imagedir city-newyork-largescale-whole.png}
}
\hfill
\subfloat[Zoom on Manhattan buildings\label{fig:city-ny-largescale-zoomB}]{%
  \includegraphics[width=0.45\textwidth]{\imagedir city-newyork-largescale-zoomB.png}
}\\
\subfloat[Focus on Manhattan\label{fig:city-ny-largescale-zoomZ}]{%
  \includegraphics[width=0.45\textwidth]{\imagedir city-newyork-largescale-zoomA.png}
}
\hfill
\subfloat[Central Park\label{fig:city-ny-largescale-zoomC}]{%
  \includegraphics[width=0.45\textwidth]{\imagedir city-newyork-largescale-zoomC.png}
}
\caption{$20 \times 20 \mathrm{km}^2\ $ geometric reconstruction of New York City (LOD-1)}
\label{fig:city-ny-largescale}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\subfloat[LOD-0\label{fig:sm-building-east}]{%
  \includegraphics[width=0.45\textwidth]{\imagedir solar-masks-east-facing.png}
}
\hfill
\subfloat[LOD-1\label{fig:sm-whole-building}]{%
  \includegraphics[width=0.45\textwidth]{\imagedir solar-masks-whole-building.png}
}\\
\subfloat[LOD-1 Large scale\label{fig:sm-strasbourg}]{%
  \includegraphics[width=0.45\textwidth]{\imagedir solar-masks-strasbourg.png}
}
\hfill
\subfloat[Heat transfer benchmark in 2D including view factors~\cite{van_eck_surface_2016}\label{fig:view-factor}]{%
  \includegraphics[width=0.45\textwidth]{\imagedir view-factors-benchmark.png}
}
\caption{Solar masks and view factors computations}
\label{fig:solar-masks-vf}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{\imagedir feelpp-devops.png}
    \caption{CI/CD DevOps for Feel++}
    \label{fig:feelpp-devops}
\end{figure}
The CI/CD workflow, see Figure~\ref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework. The workflow leverages various main ingredients of GitHub Actions features.
\begin{enumerate}
    \item \textbf{Pull Requests and Merges:} Triggering CI to verify that new code integrations meet all tests and standards.
    \item \textbf{Graphical User Interface (GUI) thanks to \texttt{workflow\_dispatch}:} Enabling developers to manually trigger pipelines through a GUI, which facilitates rapid deployment or testing. 
    \item \textbf{Scheduled Runs:} Conducting regular updates and maintenance checks to ensure continuous system integrity and responsiveness.
\end{enumerate}

@@

Figure~\ref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPCOps workflow for Feel++. 
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{\imagedir feelpp-hpcops.png}
    \caption{CI/CD HPCOps for Feel++}
    \label{fig:feelpp-hpcops}
\end{figure}

@@

\begin{wrapfigure}{R}{.7\linewidth}
    \centering
    \includegraphics[width=\linewidth]{\imagedir ub-devops.pdf}
    \caption{KUB standard DevOps}
    \label{fig:kub-devops}
\end{wrapfigure}
This framework leverages cutting-edge computational technologies, ensuring the high performance and accuracy of the Feel++ framework and Feel++-based applications. 
It sets a benchmark for integrating modern software frameworks with advanced HPC infrastructure to significantly advance computational research and applications.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{\imagedir ub-hpcops.pdf}
    \caption{Ktirio Urban Building HPCOps workflow}
    \label{fig:kub-hpcops}
\end{figure}

@@

\begin{wrapfigure}{R}{0.6\textwidth}  % Adjust 'R' and width as needed
  \centering
  \begin{subfloat}[Scalability tests on a few EuroHPC systems from 1 to 32 nodes of 128 cores per node]{
    \includegraphics[width=0.9\linewidth]{\imagedir kub-scalability.png}
    \label{fig:scalability}
  }\end{subfloat}
  \\
  \begin{subfloat}[Execution breakdown on a few EuroHPC systems from 1 to 32 nodes of 128 cores per node]{
    \includegraphics[width=0.9\linewidth]{\imagedir kub-bencharkings-execution.png}
    \label{fig:execution-breakdown}
  }\end{subfloat}
  \caption{Detailed performance metrics for scalability and execution on EuroHPC systems}
  \label{fig:combined-metrics}
\end{wrapfigure}
The pipeline's simulation part scales almost linearly, which is expected as the buildings are not coupled together in the model currently used for the simulation. On the other hand, the total execution of the pilot's pipeline does not scale; as more nodes are employed, the performance degrades.

>>>>

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth]{img-kub-workflow.pdf}
    \caption{Current Urban Building Workflow from localization to city energy simulation report.}
    \label{fig:kub-workflow}
\end{figure}

@@

\begin{wrapfigure}{R}{0.6\textwidth} % 'R' or 'L' for right or left, and width
\centering
\subfloat[LOD-0: a building is represented by its bounding box]{%
  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod0.png}
  \label{fig:building-lod0}
}
%\hfill % This ensures that the images are placed side by side
\subfloat[LOD-1: a building is represented by its ground footprint elevated to its height]{%
  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod1.png}
  \label{fig:building-lod1}
}\\ % Ends the line for the first row of figures

\subfloat[LOD-2: a building in full detail using BIM. Note that LOD-2 and LOD-1 are mixed.]{%
  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod2.png}
  \label{fig:building-lod2}
}
%\hfill
\subfloat[LOD-2: A zoom on the LOD-2 building.]{%
  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod2-zoom.png}
  \label{fig:building-lod2-zoom}
}

@@

\begin{wrapfigure}{R}{0.6\textwidth}
\centering
\subfloat[LOD-0\label{fig:city-strasbourg-lod0}]{%
  \includegraphics[width=0.4\textwidth]{img-compressed-city-strasbourg-lod-0.png}
}
\hfill % Ensures that the images are placed side by side
\subfloat[LOD-1\label{fig:city-strasbourg-lod1}]{%
  \includegraphics[width=0.4\textwidth]{img-compressed-city-strasbourg-lod-1.png}
}\\ % Ends the line for the first row of figures

\subfloat[LOD-1 terrain\label{fig:city-grenoble-terrain}]{%
  \includegraphics[width=0.4\textwidth]{img-compressed-city-grenoble-terrain.png}
}

@@

The current version of our simulation framework has implemented case 0 and case 1. Cases 2 and 3 require a full conformal mesh, which is not yet available. Moreover, these partitioning strategies are costly, so we have planned to use other third-party tools, such as Zoltan2~\cite{the_zoltan2_team_zoltan2_nodate}, to improve efficiency.
\begin{wrapfigure}{R}{0.6\textwidth}
\centering
\subfloat[Partitioning Case 0\label{fig:city-strasbourg-lod0-parts}]{%
  \includegraphics[width=0.48\linewidth]{img-compressed-city-strasbourg-lod0-parts.png}
}
%\hfill % Ensures that the images are placed side by side
\subfloat[Partitioning Case 1\label{fig:city-strasbourg-lod1-parts}]{%
  \includegraphics[width=0.48\linewidth]{img-compressed-city-strasbourg-lod1-parts.png}
}
%\subfloat[Partitioning Case 3: Large scale\label{fig:city-ny-largescale}]{%
%  \includegraphics[width=0.4\textwidth]{img-compressed-city-newyork-largescale.png}
%}
\caption{Mesh partitioning illustrations}
\label{fig:partitioning}
\end{wrapfigure}

@@

\begin{figure}[htbp]
\centering
\subfloat[View on whole 3D mesh\label{fig:city-ny-largescale-whole}]{%
  \includegraphics[width=0.45\textwidth]{img-compressed-city-newyork-largescale-whole.png}
}
\hfill
\subfloat[Zoom on Manhattan buildings\label{fig:city-ny-largescale-zoomB}]{%
  \includegraphics[width=0.45\textwidth]{img-compressed-city-newyork-largescale-zoomB.png}
}\\
\subfloat[Focus on Manhattan\label{fig:city-ny-largescale-zoomZ}]{%
  \includegraphics[width=0.45\textwidth]{img-compressed-city-newyork-largescale-zoomA.png}
}
\hfill
\subfloat[Central Park\label{fig:city-ny-largescale-zoomC}]{%
  \includegraphics[width=0.45\textwidth]{img-compressed-city-newyork-largescale-zoomC.png}
}
\caption{$20 \times 20 \mathrm{km}^2\ $ geometric reconstruction of New York City (LOD-1)}
\label{fig:city-ny-largescale}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\subfloat[LOD-0\label{fig:sm-building-east}]{%
  \includegraphics[width=0.45\textwidth]{img-compressed-solar-masks-east-facing.png}
}
\hfill
\subfloat[LOD-1\label{fig:sm-whole-building}]{%
  \includegraphics[width=0.45\textwidth]{img-compressed-solar-masks-whole-building.png}
}\\
\subfloat[LOD-1 Large scale\label{fig:sm-strasbourg}]{%
  \includegraphics[width=0.45\textwidth]{img-compressed-solar-masks-strasbourg.png}
}
\hfill
\subfloat[Heat transfer benchmark in 2D including view factors~\cite{van_eck_surface_2016}\label{fig:view-factor}]{%
  \includegraphics[width=0.45\textwidth]{img-compressed-view-factors-benchmark.png}
}
\caption{Solar masks and view factors computations}
\label{fig:solar-masks-vf}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-compressed-feelpp-devops.png}
    \caption{CI/CD DevOps for Feel++}
    \label{fig:feelpp-devops}
\end{figure}
The CI/CD workflow, see Figure~\ref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework. The workflow leverages various main ingredients of GitHub Actions features.
\begin{enumerate}
    \item \textbf{Pull Requests and Merges:} Triggering CI to verify that new code integrations meet all tests and standards.
    \item \textbf{Graphical User Interface (GUI) thanks to \texttt{workflow\_dispatch}:} Enabling developers to manually trigger pipelines through a GUI, which facilitates rapid deployment or testing. 
    \item \textbf{Scheduled Runs:} Conducting regular updates and maintenance checks to ensure continuous system integrity and responsiveness.
\end{enumerate}

@@

Figure~\ref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPCOps workflow for Feel++. 
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-compressed-feelpp-hpcops.png}
    \caption{CI/CD HPCOps for Feel++}
    \label{fig:feelpp-hpcops}
\end{figure}

@@

\begin{wrapfigure}{R}{.7\linewidth}
    \centering
    \includegraphics[width=\linewidth]{img-ub-devops.pdf}
    \caption{KUB standard DevOps}
    \label{fig:kub-devops}
\end{wrapfigure}
This framework leverages cutting-edge computational technologies, ensuring the high performance and accuracy of the Feel++ framework and Feel++-based applications. 
It sets a benchmark for integrating modern software frameworks with advanced HPC infrastructure to significantly advance computational research and applications.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-ub-hpcops.pdf}
    \caption{Ktirio Urban Building HPCOps workflow}
    \label{fig:kub-hpcops}
\end{figure}

@@

\begin{wrapfigure}{R}{0.6\textwidth}  % Adjust 'R' and width as needed
  \centering
  \begin{subfloat}[Scalability tests on a few EuroHPC systems from 1 to 32 nodes of 128 cores per node]{
    \includegraphics[width=0.9\linewidth]{img-compressed-kub-scalability.png}
    \label{fig:scalability}
  }\end{subfloat}
  \\
  \begin{subfloat}[Execution breakdown on a few EuroHPC systems from 1 to 32 nodes of 128 cores per node]{
    \includegraphics[width=0.9\linewidth]{img-compressed-kub-bencharkings-execution.png}
    \label{fig:execution-breakdown}
  }\end{subfloat}
  \caption{Detailed performance metrics for scalability and execution on EuroHPC systems}
  \label{fig:combined-metrics}
\end{wrapfigure}
The pipeline's simulation part scales almost linearly, which is expected as the buildings are not coupled together in the model currently used for the simulation. On the other hand, the total execution of the pilot's pipeline does not scale; as more nodes are employed, the performance degrades.
